The Astropy Project

### 2017-11-22 main.tex
remove distribution section and add setence to release section

\subsection{Distribution of packages}

The \astropypkg core package is available from several of the \python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
%
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
%
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package
Index\footnote{\url{https://pypi.org/project/astropy}} (PyPI)
using \texttt{pip}, the standard command-line tool for installing \python packages.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.
% hamogu: I think that's too detailed for a journal paper.
%     It's in the docs if anyone needs it.
%Optionally, the version of
%the package and the dependencies needed to run or build the software are given
%by a specifier to the pip package manager as described in PEP 440\footnote{For
%more detailed installation instructions and optional flags see
%\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.

Packaged versions of \astropy are also available for several
operating systems that are managed by a system's package manager,
including Debian, Ubuntu, Fedora, Gentoo, Arch Linux, Mac OS X (e.g.,
via brew, macports or fink) and FreeBSD\@.  However, on occasion these packages
may be outdated compared with the latest stable release of \astropy accessible
from the PyPI\@. Pre-built binary conda packages for all of the affiliated packages are also available  via the \texttt{astropy} conda channel for Linux, Mac OS X, and MS Windows.
% * <mattwcraig@gmail.com> 2017-10-27T07:16:27.310Z:
%
% > re-built binary conda packages
% Feel free to remove if this is too detailed. I do think the available of the whole ecosystem across all platforms has helped speed its adoption.
%
% ^.

>>>>

The released versions of the \astropypkg core package are available from several
of the \python distributions for scientific computing (e.g.,
\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
(PyPI).\footnote{See the installation documentation for more information:
\url{http://docs.astropy.org/en/stable/install.html}}
